---
title: "R Notebook"
output:
  html_document:
    toc: yes
    df_print: paged
    theme: flatly
    fig_caption: yes
    number_sections: yes
    code_folding: hide
bibliography: bib.bib
csl: plos.csl
---

---

# . Video tracking

The bots trajectory were extracted from the experimental videos using the
`trackR` function in the `trackR` package (version 0.3.2) @trackr2020 for R. The
parameters of the video-tracking were set individually for each video so as to
maximize the automated tracking accuracy of each experiments. The resulting
trajectories were then manually inspected and corrected for defects (e.g.,
swapped IDs, spurious trajectories, disconnected trajectories, etc) using the
`trackFixer` function of the `trackR` package.

```{r message=FALSE}
library(readr)
if (!require(trackdf, quietly = TRUE)) {
  remotes::install_github("swarm-lab/trackdf")
} else if (packageVersion("trackdf") < "0.2.2") {
  remotes::install_github("swarm-lab/trackdf")
}
library(trackdf)
library(dplyr)

tracks <- read_rds("data_WT.rds") %>%
  filter(., ignore == FALSE) 
```

This resulted in a total of `r format(nrow(tracks), big.mark = ",")` unique
positions grouped into `r format(length(unique(tracks$id)), big.mark = ",")`
unique trajectories.

---

# . Basic movement metrics

For each position of each trajectory, we calculated the following metrics:

```{r}
tracks <- tracks %>%
  group_by(., id) %>%
  arrange(., t, .by_group = TRUE)
```

- The linear distance between the current position and the immediately preceding 
one. By convention, the linear distance is set to 0 for the first position.

```{r message=FALSE}
if (!require(swaRm, quietly = TRUE)) {
  remotes::install_github("swarm-lab/swaRm")
}
library(swaRm)

tracks <- tracks %>%
  mutate(., lin_dist = linDist(x, y))
```

- The linear speed at each position, approximated as the distance moved between 
the current position and the immediately preceding one during the time interval 
between these 2 positions. Note that a linear speed can, therefore, not be 
calculated for the first position.

```{r}
tracks <- tracks %>%
  mutate(., lin_speed = linSpeed(x, y, t))
```

- The heading of the bot at each position, approximated as the angle between the 
vector formed by the current position and the immediately preceding one and that 
formed by the current position and the immediately following one. Note that a 
heading can, therefore, not be calculated for the first position.

```{r}
tracks <- tracks %>%
  mutate(., heading = heading(x, y))
```

- The angular speed of the bot at each position, approximated as the difference 
between the heading at the immediately preceding position and that at the current 
one during the time interval between the corresponding 3 positions required to 
calcutate these 2 headings (see previous point). Note that an angular speed can, 
therefore, not be calculated for the first two positions.

```{r}
tracks <- tracks %>%
  mutate(., ang_speed = angSpeed(x, y, t))
```

- The time difference between each position.

```{r}
tracks <- tracks %>%
  mutate(., dt = as.numeric(diff(c(t, NA)), units = "secs")) %>%
  ungroup(.)
```

---

# . Behavioral classification

Behavioral classification was performed on non-overlapping 30-second chunks of
trajectory.

## . Active vs inactive

Visual inspection of the experimental videos suggested that bots spent a
significant amount of time motionless. Therefore, we started our analysis by
classifying the 30-second chunks of trajectory into active and inactive chunks.

Because of various sources of uncertainties in our observation and tracking
protocol, it is not reliable to only use instantaneous speed as a metric to
separate active from inactive chunks of trajectory. For instance, slow directed
movement may not always be distinguishable from random position shifts due to
tracking uncertainty using speed as the only differentiating metric.

In order to circumvent this issue, we defined activity as predictable movement,
that is a sequence of successive position changes that are not fully independent
from each other.

To determine how predictable a position change was, we used the linear speed,
heading, and angular speed estimated at each position to predict the coordinates
of the following position. We then computed the error (Euclidean distance)
between the predicted coordinates and the actual coordinates.

```{r}
tracks <- tracks %>%
  group_by(., id) %>%
  arrange(., t, .by_group = TRUE) %>%
  mutate(., pred_x = x + (lin_speed * dt * cos(heading + ang_speed)),
         pred_y = y + (lin_speed * dt * sin(heading + ang_speed)),
         error = c(NA, sqrt((x[2:n()] - pred_x[1:(n() - 1)]) ^ 2 + 
                              (y[2:n()] - pred_y[1:(n() - 1)]) ^ 2))) %>%
  ungroup(.) 
```

For each complete 30-second chunk of trajectory (i.e. chunks with no missing
time stamp), we then calculated the total error over the entire chunk and
normalized it by the total distance traveled during that chunk in order to
account for the artificial error amplification caused by predicting over longer
distances. We also discarded all chunks that have at least one point within 0.5
mm of the arena wall in order to eliminate edge effects on the bots' behaviors.

```{r fig.width=6, fig.height=6, out.width='50%'}
library(ggplot2)

chunk_size <- 30 

tracks <- tracks %>%
  group_by(., id) %>%
  mutate(., group = (as.numeric(t - min(t), units = "secs") - 
                       (as.numeric(t - min(t), units = "secs") %% 
                          chunk_size)) / chunk_size) %>%
  ungroup(.)

activity_summ <- tracks %>%
  group_by(., id, group) %>%
  summarize(., norm_error = sum(error, na.rm = TRUE) / sum(lin_dist, na.rm = TRUE),
            n = n(), 
            discard = any(arena_dist < 0.05),
            .groups = "drop") %>%
  ungroup(.) %>%
  filter(., n == chunk_size) 

ggplot(filter(activity_summ, discard == FALSE), aes(norm_error)) +
  geom_histogram(aes(y = ..density..), bins = 100, alpha = 0.5) +
  labs(x = "Total normalized error", y = "Density") +
  theme_light(base_size = 16, base_family = "Raleway")
```

In order to separate active from inactive chunks, we applied an automated
classification method on the distribution of total normalized errors. We fit a
Gamma mixture model with 2 components to the data using the expectation
maximization algorithm in the `REBMIX` function from the `rebmix` package
(version 2.12.0) @rebmix2020 for R.

```{r fig.height=6, fig.width=6, out.width='50%', message=FALSE, cache=TRUE}
library(rebmix)

gmix <- activity_summ %>%
  filter(., discard == FALSE) %>%
  dplyr::select(., norm_error) %>%
  list(df = .) %>%
  REBMIX(Dataset = ., pdf = "gamma", Preprocessing = "histogram",
         cmin = 2, cmax = 2, Criterion = "BIC")

ggplot(filter(activity_summ, discard == FALSE), aes(norm_error)) +
  geom_histogram(aes(y = ..density..), bins = 100, alpha = 0.5) +
  stat_function(fun = function(x, shape, scale, lambda) dgamma(x, shape = shape, scale = scale) * lambda,
                args = list(shape = gmix@Theta[[1]]$theta2.1, 
                            scale = gmix@Theta[[1]]$theta1.1, 
                            lambda = gmix@w[[1]][1]),
                n = 1001, color = "#1B9E77", size = 1) +
  stat_function(fun = function(x, shape, scale, lambda) dgamma(x, shape = shape, scale = scale) * lambda,
                args = list(shape = gmix@Theta[[1]]$theta2.2, 
                            scale = gmix@Theta[[1]]$theta1.2, 
                            lambda = gmix@w[[1]][2]),
                n = 1001, color = "#D95F02", size = 1) +
  labs(x = "Total normalized error", y = "Density") +
  theme_light(base_size = 16, base_family = "Raleway")
```

The 30-second chunks in the resulting cluster with the highest total normalized
error were considered as inactive and excluded from further classification. The
chunks in the other cluster were considered as active and subjected to further
classification to determine their behavioral properties (see below).

```{r message=FALSE}
cl <- factor(rebmix::RCLRMIX(x = gmix)@Zp)
mus <- c(gmix@Theta[[1]]$theta1.1 * gmix@Theta[[1]]$theta2.1,
         gmix@Theta[[1]]$theta1.2 * gmix@Theta[[1]]$theta2.2)

activity_class <- activity_summ %>%
  filter(., discard == FALSE) %>%
  mutate(., activity = if_else(cl == which.max(mus) | norm_error > max(mus), 
                               "inactive", "active")) %>%
  dplyr::select(., id, group, activity)
```

## . Movement patterns

Preliminary observations of the recorded tracks suggested that the bots'
movements could be described as a combination of straight lines and circles (or
arcs).

We therefore defined the following two indices to capture the most common path
classes displayed by the bots during each chunk: 

- A "straightness" inde computed as one minus the circular variance of the 
headings during the chunk. A value of 1 indicates a perfectly straight line. 

- A "gyration" index computed as one minus the circular variance of the angular 
speeds during the chunk divided by the circular variance of the angular speeds 
if they were distributed symmetrically around zero. A value of 1 indicates a 
trajectory following a perfect circle.

```{r message=FALSE}
library(circular)

behavior_summ <- tracks %>%
  full_join(., activity_class, by = c("id", "group")) %>%
  filter(., activity == "active") %>%
  mutate(., heading = as.circular(heading, type = "angles", units = "radians",
                                  template = "none", modulo = "asis", 
                                  rotation = "counter", zero = 0),
         ang_speed = as.circular(ang_speed, type = "angles", units = "radians",
                                 template = "none", modulo = "asis", 
                                 rotation = "counter", zero = 0)) %>%
  group_by(., id, group) %>%
  summarize(., straightness = 1 - var.circular(heading, na.rm = TRUE),
            gyration = 1 - (var.circular(c(ang_speed, ang_speed), na.rm = TRUE) /
                              var.circular(c(ang_speed, -ang_speed), na.rm = TRUE)),
            .groups = "drop")
```

The distributions of the two indices are represented below.

```{r fig.height=6, fig.width=12}
library(patchwork)

g1 <- ggplot(behavior_summ, aes(x = straightness)) +
  geom_histogram(aes(y = ..density..), alpha = 0.5, bins = 100) +
  geom_density() + 
  labs(x = "Straightness index",
       y = "Density") +
  theme_light(base_size = 16, base_family = "Raleway")

g2 <- ggplot(behavior_summ, aes(x = gyration)) +
  geom_histogram(aes(y = ..density..), alpha = 0.5, bins = 100) +
  geom_density() + 
  labs(x = "Gyration index",
       y = "Density") +
  theme_light(base_size = 16, base_family = "Raleway")

g3 <- ggplot(behavior_summ, aes(x = straightness, y = gyration)) +
  geom_vline(xintercept = 0.5, linetype = 2, alpha = 0.5) +
  geom_hline(yintercept = 0.5, linetype = 2, alpha = 0.5) +
  geom_point(aes(color = straightness - gyration), alpha = 0.1) +
  geom_density_2d(alpha = 0.5, color = "black") +
  labs(x = "Straightness index", 
       y = "Gyration index") +
  scale_color_viridis_c(option = "inferno") +
  theme_light(base_size = 16, base_family = "Raleway") +
  theme(legend.position = "none")

g <- (g1 / g2) | g3
g <- g + 
  plot_annotation(tag_levels = "A", 
                  theme = theme(plot.tag = element_text(margin = margin(r = 10, b = 10))))
g
```

The behavioral space formed by the straightness and gyration indices defines
two behavioral extremes: 

- Top-left: purely circling trajectories. 
- Bottom-right: completely straight trajectories. 

The rest of the space represents trajectories that are relative combinations of 
these two extremes. In order to separate the trajectory chunks into categories of 
- roughly - similar behavior, we used the cross-entropy clustering algorithm 
described in @Tabor2014-kd and implemented in the `cec` function of the `CEC` 
package (version 0.10.2) @cec2018 for R. We seeded the algorithm with 9 initial 
cluster centers placed at the 4 corners of the behavioral space, at all 
mid-points between the 4 corners, and at the center of the behavioral space. 
Resulting clusters with cardinality less than 5% of the available data points 
were removed. The resulting clusters ordered by average dissimilarity (a measure 
of the internal consistency of a cluster) are displayed in the figure below. 

```{r fig.height=6, fig.width=12}
library(CEC)
library(cluster)
library(ggforce)
library(RColorBrewer)

init <- matrix(ncol = 2, byrow = TRUE,
               c(0, 0,
                 1, 0,
                 0, 1,
                 1, 1,
                 0.5, 0.5,
                 0, 0.5,
                 0.5, 0,
                 1, 0.5,
                 0.5, 1))

clusters <- behavior_summ %>%
  dplyr::select(., straightness, gyration) %>%
  as.matrix(.) %>%
  cec(., init, iter.max = 1000)

behavior_class <- behavior_summ %>%
  dplyr::select(., id, group) %>%
  mutate(., class = clusters$cluster)

class_stats <- behavior_summ %>%
  full_join(., behavior_class, by = c("id", "group")) %>%
  group_by(., class) %>%
  summarize(., size = n(),
            av_diss = daisy(cbind(straightness, gyration)) %>%
              as.matrix(.) %>%
              apply(., 1, mean) %>%
              min(.),
            med_straightness = median(straightness),
            up_straightness = quantile(straightness, 3/4),
            lo_straightness = quantile(straightness, 1/4),
            med_gyration = median(gyration),
            up_gyration = quantile(gyration, 3/4),
            lo_gyration = quantile(gyration, 1/4),
            .groups = "drop") %>%
  mutate(., behavior = rank(av_diss))

behavior_class <- behavior_class %>%
  full_join(., class_stats %>% select(., class, behavior), by = "class")

cov2shape <- function(sigma, mu) {
  eig <- eigen(sigma)
  eigval <- eig$values
  eigvec <- eig$vectors
  eigidx <- order(eigval)
  
  if (eigidx[1] == 1) {
    a <- 2 * sqrt(eigval[2])
    b <- 2 * sqrt(eigval[1])
  } else {
    a <- 2 * sqrt(eigval[1]);
    b <- 2 * sqrt(eigval[2]);
  }
  
  alpha <- atan(eigvec[2, 1] / eigvec[2, 2])
  
  c(x = mu[1], y = mu[2], alpha = alpha, a = a, b = b)
}

ellipses <- t(mapply(cov2shape, clusters$covariances, asplit(clusters$centers, 1), 
                     SIMPLIFY = TRUE)) %>%
  as_tibble(.) %>%
  mutate(., class = 1:max(behavior_class$class)) %>%
  full_join(., class_stats %>% select(., class, behavior), by = "class")

g1 <- ggplot(class_stats, aes(y = av_diss, x = factor(behavior), fill = factor(behavior))) +
  geom_col() +
  labs(x = "Behavioral cluster",
       y = "Average dissimilarity") +
  scale_fill_manual(values = c(brewer.pal(8, "Dark2"), "#333333")) +
  theme_light(base_size = 16, base_family = "Raleway") +
  theme(legend.position = "none")

g2 <- ggplot(class_stats, aes(y = 100 * size / sum(size), x = factor(behavior), fill = factor(behavior))) +
  geom_col() +
  labs(x = "Behavioral cluster",
       y = "% of observations") +
  scale_fill_manual(values = c(brewer.pal(8, "Dark2"), "#333333")) +
  theme_light(base_size = 16, base_family = "Raleway") +
  theme(legend.position = "none")

g3 <- ggplot() +
  geom_vline(xintercept = 0.5, linetype = 2, alpha = 0.5) +
  geom_hline(yintercept = 0.5, linetype = 2, alpha = 0.5) +
  geom_point(aes(x = straightness, y = gyration, color = factor(behavior)), 
             data = behavior_summ %>% full_join(., behavior_class, by = c("id", "group")), 
             alpha = 0.1) +
  geom_ellipse(aes(x0 = x, y0 = y, a = a, b = b, angle = alpha, col = factor(behavior)),
               data = ellipses, size = 1, alpha = 0.5) +
  # geom_polygon(aes(V1, V2, color = factor(behavior)), data = chull, fill = NA) +
  geom_errorbar(aes(x = med_straightness, ymin = lo_gyration, ymax = up_gyration),
                data = class_stats) + 
  geom_errorbarh(aes(y = med_gyration, xmin = lo_straightness, xmax = up_straightness),
                 data = class_stats) +
  geom_label(aes(x = med_straightness, y = med_gyration, label = behavior), 
             data = class_stats, size = 3) +
  coord_equal(xlim = c(0, 1), ylim = c(0, 1)) +
  scale_color_manual(values = c(brewer.pal(8, "Dark2"), "#333333")) +
  labs(x = "Straightness index",
       y = "Gyration index") +
  theme_light(base_size = 16, base_family = "Raleway") +
  theme(legend.position = "none")

g <- (g1 / g2) | g3
g <- g + 
  plot_annotation(tag_levels = "A", 
                  theme = theme(plot.tag = element_text(margin = margin(r = 10, b = 10))))
g
```

The final classification resulted in five categories, three of them (1, 2, 3) 
with high internal consistency (i.e., low average dissimilarity) and the other 
two (4 and 5) being more diffuse. Two of the five categories (1 and 4) represent 
more than 60% of the active chunks, indicating that the bots' most common 
behavior is to perform circling movements (categories 1 and 4 have the highest 
gyration indices of the five behavioral categories). 

## . Behavioral statistics by category

Below are behavioral statistics for each behavioral category, including the 
inactive chunks. 

```{r fig.height=4, fig.width=12}
final_behavior_summ <- tracks %>%
  full_join(., activity_class, by = c("id", "group")) %>%
  full_join(., behavior_class, by = c("id", "group")) %>%
  filter(., !is.na(activity)) %>%
  mutate(., behavior = as.character(behavior)) %>%
  mutate(., behavior = if_else(is.na(behavior), "Inactive", behavior)) %>%
  mutate(., heading = as.circular(heading, type = "angles", units = "radians",
                                  template = "none", modulo = "asis", 
                                  rotation = "counter", zero = 0),
         ang_speed = as.circular(ang_speed, type = "angles", units = "radians",
                                 template = "none", modulo = "asis", 
                                 rotation = "counter", zero = 0)) %>%
  group_by(., id, group) %>%
  summarize(., straightness = 1 - var.circular(heading, na.rm = TRUE),
            gyration = 1 - (var.circular(c(ang_speed, ang_speed), na.rm = TRUE) /
                              var.circular(c(ang_speed, -ang_speed), na.rm = TRUE)),
            lin_speed = mean(lin_speed, na.rm = TRUE),
            behavior = behavior[1],
            .groups = "drop")

g1 <- ggplot(final_behavior_summ, aes(x = factor(behavior), y = straightness, 
                                      fill = factor(behavior))) +
  geom_boxplot() +
  labs(x = "Behavioral cluster",
       y = "Straightness index") +
  scale_fill_manual(values = c(brewer.pal(8, "Dark2"), "#333333")) +
  theme_light(base_size = 16, base_family = "Raleway") +
  theme(legend.position = "none")

g2 <- ggplot(final_behavior_summ, aes(x = factor(behavior), y = gyration, 
                                      fill = factor(behavior))) +
  geom_boxplot() +
  labs(x = "Behavioral cluster",
       y = "Gyration index") +
  scale_fill_manual(values = c(brewer.pal(8, "Dark2"), "#333333")) +
  theme_light(base_size = 16, base_family = "Raleway") +
  theme(legend.position = "none")

g3 <- ggplot(final_behavior_summ, aes(x = factor(behavior), y = lin_speed, 
                                      fill = factor(behavior))) +
  geom_boxplot() +
  labs(x = "Behavioral cluster",
       y = "Linear speed") +
  scale_fill_manual(values = c(brewer.pal(8, "Dark2"), "#333333")) +
  theme_light(base_size = 16, base_family = "Raleway") +
  theme(legend.position = "none")

g <- g1 | g2 | g3
g <- g + 
  plot_annotation(tag_levels = "A", 
                  theme = theme(plot.tag = element_text(margin = margin(r = 10, b = 10))))
g
```

## . Trajectory samples for each category

Below are sample trajectories for each behavioral category, including the 
inactive chunks. The grid size of each plot is indicative of the relative scale 
of trajectories. 

```{r fig.height=8, fig.width=12}
library(tidyr)

tracks_cl <- tracks %>%
  full_join(., activity_class, by = c("id", "group")) %>%
  full_join(., behavior_class, by = c("id", "group")) %>%
  filter(., !is.na(activity)) %>%
  mutate(., behavior = as.character(behavior)) %>%
  mutate(., behavior = if_else(is.na(behavior), "Inactive", behavior))

tracks_sample <- tracks_cl %>%
  group_by(., behavior, id, group, condition) %>%
  nest(.) %>%
  group_by(., behavior) %>%
  do(., sample_n(., 9)) %>%
  unnest(., data) %>%
  group_by(., behavior, id, group, condition) %>%
  mutate(., x = x - mean(x), y = y - mean(y)) %>%
  ungroup(.)

g <- tracks_sample %>%
  group_by(., behavior, id, group) %>%
  do(., g = ggplot(., aes(x, y)) +
       geom_path() +
       coord_fixed(xlim = range(c(.$x, .$y)), ylim = range(c(.$x, .$y))) +
       scale_x_continuous(breaks = seq(-0.3, 0.3, 0.01)) +
       scale_y_continuous(breaks = seq(-0.3, 0.3, 0.01)) +
       theme_light(base_size = 16, base_family = "Raleway")  +
       theme(axis.title = element_blank(),
             axis.text = element_blank(),
             axis.ticks = element_blank())) %>%
  ungroup(.) %>%
  group_by(., behavior) %>%
  do(., g = wrap_plots(.$g, nrow = 3) +
       plot_annotation(title = paste0("Category ", .$behavior[1]),
                       theme = theme(plot.title = element_text(size = 16, family = "Raleway")))) %>%
  ungroup(.) 

wrap_elements(g$g[[1]]) + wrap_elements(g$g[[2]]) + wrap_elements(g$g[[3]]) +
  wrap_elements(g$g[[4]]) + wrap_elements(g$g[[5]]) + wrap_elements(g$g[[6]])
```

---

# . Behavioral transitions

In order to understand better how the bots' behaviors are distributed relative 
to each other, we estimated the transition probabilities between each behavioral
category by calculating the proportion of times a chunk of a given category is 
followed by a chunk of the same or another category. In order to simplify the 
interpretation of the resulting behavioral transition network, we: 

- grouped chunks from categories 1 and 4 together under a new category called 
"Gyrating";
- grouped chunks from categories 2 and 3 together under a new category called 
"Non-gyrating";
- renamed category 5 as "Intermediary".

```{r message=FALSE}
library(msm)
library(tidygraph)

sub2ind <- function(row, col, nrow) {
  (col - 1) * nrow + row
}

freqTable <- function(state, id, levels) {
  x <- statetable.msm(state, id)
  m <- matrix(0, nrow = length(levels), ncol = length(levels))
  colnames(m) <- levels
  rownames(m) <- levels
  idx <- expand.grid(which(levels %in% rownames(x)), which(levels %in% rownames(x)))
  m[sub2ind(idx[, 1], idx[, 2], nrow = length(levels))] <- x
  m
}

graphTable <- function(freq, relative = FALSE) {
  if (relative == TRUE) {
    t_tb <- t(apply(freq, 1, function(x) x / sum(x)))
    t_tb[is.na(t_tb)] <- 0
  } else {
    t_tb <- freq
  }
  
  tbl_graph(nodes = data.frame(name = rownames(freq), count = apply(freq, 1, sum)),
            edges = as.data.frame(cbind(which(t_tb > -1, arr.ind = TRUE), weight = as.vector(t_tb))))
}

final_behavior_summ <- final_behavior_summ %>%
  mutate(., behavior_simplified = if_else(behavior == "1" | behavior == "4", "Gyrating",
                                          if_else(behavior == "2" | behavior == "3", "Non-gyrating",
                                                  if_else(behavior == "5", "Intermediary", behavior))))

freq_table <- freqTable(final_behavior_summ$behavior_simplified, final_behavior_summ$id,
                        levels = sort(unique(final_behavior_summ$behavior_simplified)))
graph_table <- graphTable(freq_table, relative = TRUE)
```

The estimated transition network is represented below. Note in particular that 
the bots never transitioned directly from the "Inactive" category to the 
"Gyrating" one, and vice versa, and always had to go through one of the other 
two categories first. 

```{r message=FALSE, fig.height=6, fig.width=6}
library(ggraph)
library(scales)

graph_table %>% 
  activate(edges) %>% 
  filter(weight > 0) %>%
  ggraph(., layout = "linear", circular = TRUE) + 
  geom_edge_fan(aes(label = percent(weight, accuracy = 0.01, digits = 0), 
                    edge_alpha = weight),
                arrow = arrow(length = unit(3, "mm")),
                start_cap = circle(15, "mm"),
                end_cap = circle(15, "mm"),
                angle_calc = "along",
                label_dodge = unit(-3, "mm")) + 
  geom_edge_loop(aes(label = percent(weight, accuracy = 0.01, digits = 0), 
                     edge_alpha = weight, span = 60, strength = 0.75, 
                     direction = c(45, 0, 0, -45, 0, 0, 0, 0, -135, 0, 0, 0, 0, 135)),
                 arrow = arrow(length = unit(3, "mm")),
                 start_cap = circle(15, "mm"),
                 end_cap = circle(15, "mm"),
                 angle_calc = "along",
                 label_dodge = unit(-3, "mm")) +
  geom_node_point(size = 35) +
  geom_node_text(aes(label = paste0(name, "\n", count)), color = "white") +
  scale_x_continuous(expand = expansion(c(.12, .12))) +
  scale_y_continuous(expand = expansion(c(.12, .12))) + 
  theme(legend.position = "none",
        panel.background = element_rect(fill = "white"))

```

---

# References

